### 2020-02-29 ChapterProblemDefinition/chapterProblemDefinition.tex
Updated: Description for aura size graphs and predictions
Updated: Made mentions of consistency in Proposed Solution

@@

The aura of an object can then be calculated using the following equation: 
\begin{equation}
R_{a}=R_{o}+(V_{t}\cdot T_{T})
\end{equation}
$R_{a}$ is the radius of the aura in $m$, $R_{o}$ is the bounding sphere of the object, $V_{t}$ is the speed tolerance in $m\mathord{\cdot}s^{-1}$ and $T_{T}$ is the total $Max_{DT}$ in $s$.

>>>>

In summary, objects that are being hosted by a remote server are consistency-aware, through the use of auras. The system doesn't know exactly where the object will be, but can guarantee it will be within the aura by the time an interaction takes place.
A small amount of availability is sacrificed (in the region of 10ms) as objects migrate between servers, in order to achieve eventual consistency while maintaining network partitioning.
In terms of collisions between objects, AP provides strong consistency. All collisions between objects only take place on a single server, removing the possibility of inconsistencies between servers. Network partitioning is sacrificed in order to achieve strong consistency.% and no sacrifice to availability is made.

@@

The aura of an object can then be calculated using the following equation: 
\begin{equation}\label{auraEquation}
R_{a}=R_{o}+(V_{t}\cdot T_{T})
\end{equation}
$R_{a}$ is the radius of the aura in $m$, $R_{o}$ is the bounding sphere of the object, $V_{t}$ is the speed tolerance in $m\mathord{\cdot}s^{-1}$ and $T_{T}$ is the total $Max_{DT}$ in $s$.
